From Reversible Programs to \\ Univalent Universes and Back

### 2021-05-10 Pi+/paper/equivalence.tex
Outline text in section 5
Add more text in sec 5
Fixes #105

First, we normalise $\PiPlusLang$ to $\PiHatLang$, and show that they are equivalent.

@@

@@

Finally, we show how to translate $\PiLang$ programs to $\PiPlusLang$ programs.

>>>>

\subsection{$\PiLang$ to $\PiPlusLang$}

We show how to translate $\PiLang$ programs to $\PiPlusLang$ programs.

\subsection{$\PiPlusLang$ to $\PiHatLang$}

We normalise $\PiPlusLang$ to $\PiHatLang$, and show that they are equivalent.

\begin{definition}
  \begin{align*}
    \evalh_{0} & : \UPlus n \to \UHat n \\
    \evalh_{1} & : (c : t_{1} \iso t_{2}) \to \evalh_{0}(t_{1}) \isoh \evalh_{0}(t_{2}) \\
    \evalh_{2} & : (\alpha : c_{1} \Iso c_{2}) \to \evalh_{1}(c_{1}) \Isoh \evalh_{1}(c_{2}) \\
  \end{align*}
\end{definition}

\begin{definition}
  \begin{align*}
    \quoteh_{0} & : \UHat n \to \UPlus n \\
    \quoteh_{1} & : (p : X_{1} \isoh X_{2}) \to \quoteh_{0}(X_{1}) \iso \quoteh_{0}(X_{2}) \\
    \quoteh_{2} & : (\alpha : p_{1} \Isoh p_{2}) \to \quoteh_{1}(p_{1}) \Iso \quoteh_{1}(p_{2}) \\
  \end{align*}
\end{definition}

\subsection{$\PiHatLang$ to $\UFin$}

@@

\begin{definition}
  \begin{align*}
    \evalt_{0} & : \UHat n \to \UFin[n] \\
    \evalt_{1} & : (c : t_{1} \isoh t_{2}) \to \evalh_{0}(t_{1}) \id \evalh_{0}(t_{2}) \\
    \evalt_{2} & : (\alpha : c_{1} \Isoh c_{2}) \to \evalt_{1}(c_{1}) \id \evalt_{1}(c_{2}) \\
  \end{align*}
\end{definition}

\begin{definition}
  \begin{align*}
    \quotet_{0} & : \UFin[n] \to \UHat n \\
    \quotet_{1} & : (p : X_{1} \id X_{2}) \to \quoteh_{0}(X_{1}) \isoh \quoteh_{0}(X_{2}) \\
    \quotet_{2} & : (\alpha : p_{1} \id p_{2}) \to \quoteh_{1}(p_{1}) \Isoh \quotet_{1}(p_{2}) \\
  \end{align*}
\end{definition}

@@

\begin{definition}
  \begin{align*}
    \evalt_{0} & : \UPlus n \to \UFin[n] \\
    \evalt_{1} & : (c : t_{1} \iso t_{2}) \to \evalt_{0}(t_{1}) \id \evalt_{0}(t_{2}) \\
    \evalt_{2} & : (\alpha : c_{1} \Iso c_{2}) \to \evalt_{1}(c_{1}) \id \evalt_{1}(c_{2}) \\
  \end{align*}
\end{definition}

\begin{definition}
  \begin{align*}
    \quotet_{0} & : \UFin[n] \to U n \\
    \quotet_{1} & : (p : X_{1} \id X_{2}) \to \quotet_{0}(X_{1}) \iso \quotet_{0}(X_{2}) \\
    \quotet_{2} & : (\alpha : p_{1} \id p_{2}) \to \quotet_{1}(p_{1}) \Iso \quotet_{1}(p_{2}) \\
  \end{align*}
\end{definition}

\begin{theorem}
  ${\quotet}/{\evalt}$ gives a symmetric monoidal equivalence between $\UPlus$
  and $\UFin$.
\end{theorem}
